\textbf{SuGaLi: A Quest to Identify the Languages of the World}

### 2014-01-18 docs/The Adventures of Sugali.tex
pardon the language ;P

\emph{``Behold, the language code is one, and they have all one ISO code; and this they begin to do: and now nothing will be restrained from them, which they have imagined to do. Go to, let us go down, and there confound their ISO codes, that they may not differentiate one another's text."} - The Tower of Sugarlike.

>>>>

\emph{``Behold, the language code is one, and they have all one ISO; and this they begin to do: and now nothing will be restrained from them, which they have imagined to do. Go to, let us go down, and there confound their ISOs, that they may not differentiate one another's text."} - The Tower of Sugarlike.
